Light Transport Techniques for Tensor Field Visualization

### 2019-07-31 beamer2thesis/dummy.tex
update

\begin{document}

@@

\frame{
\frametitle{{Propagation Scheme - Physical Model}}
\begin{block}{\centering \textbf{Crystal Fiber Structures}}
\begin{itemize}
	\item crystal lattices reveal gradients dependent on direction, which leads to anisotropic light transport inside the medium (birefringence)
	\item the propability for redistribution of a photon in a particular direction is given by the phase function model yielded from Rayleigh scattering:
	\begin{align*}
 	P(\omega) &= \frac{T(\omega)}{\int_{k\pi}^{(k+1)\pi}T(\omega)\mathop{d\omega}}\\
 	\mathit{with} \int_0^{\pi} P(\omega) &= 1.
	\end{align*}
	\item each tensor is then a unique footprint: $t_{i,j}\mapsto T(\omega)$
\end{itemize}
\end{block}
} % END OF FRAME

>>>>

\renewcommand\thempfootnote{\arabic{mpfootnote}}
\begin{document}

@@

\frame{
\frametitle{{Tensor Fields - Tensor Field Lines}}

\begin{columns}
\begin{column}{.6\textwidth}
\begin{small}
\begin{block}{\centering \textbf{Procedure}}
follow major/minor eigenvectors along pathlines
\end{block}
\end{small}
\bigskip
\begin{small}
\begin{itemize}
	\item ambiguity for nearly isotropic cases:\\ small changes in components effect large changes in tensor field line orientation (see Fig.)
	\item therefore susceptive to noise in data
	\item trajectories can cross each other\\
	$\Rightarrow$ effects erroneous trajectories, hard to interpret
\end{itemize}
\end{small}

\end{column}
\begin{column}{.4\textwidth}
\centering
\begin{figure}[t]
\centering
\includegraphics[height=0.8\textwidth]{nearly_isotropic.pdf}
\caption*{Ambiguity}
\end{figure}

\end{column}
\end{columns}
} % END OF FRAME
